---
title: "Data cleaning and analysis by Luyang"
output: html_notebook
---



```{r}
setwd("/Users/luyang/Downloads") 
getwd()
PL=read.csv("PL.csv")
```
```{r}
#Filter out all incomplete data#
PL=na.omit(PL)
```


```{r}
#Convert Physical Activity day to 0-7#
PL$Vig_Day = PL$Vig_Day -1
PL$Mod_Day = PL$Mod_Day -1
PL$Walk_Day = PL$Walk_Day -1
```


```{r}
#Convert Physical Activity to a general index#
PL$Walk_MET= 3.3 * PL$Walk_Time * PL$Walk_Day
PL$Mod_MET= 4.0 * PL$Mod_Time * PL$Mod_Day
PL$Vig_MET= 8.0 * PL$Vig_Time * PL$Vig_Day
PL$PhyAct=PL$Walk_MET+PL$Mod_MET+PL$Vig_MET
```

```{r}
#Reverse Coding for Loneliness Scale#
PL$Lone_1= 5-PL$Lone_1
PL$Lone_2= 5-PL$Lone_2
PL$Lone_3= 5-PL$Lone_3
PL$Lone_4= 5-PL$Lone_4
PL$Lone_5= 5-PL$Lone_5
PL$Lone_6= 5-PL$Lone_6
PL$Lone_7= 5-PL$Lone_7
PL$Lone_8= 5-PL$Lone_8
PL$Lone_9= 5-PL$Lone_9
PL$Lone_10= 5-PL$Lone_10
PL$Lone_11= 5-PL$Lone_11
PL$Lone_12= 5-PL$Lone_12
PL$Lone_13= 5-PL$Lone_13
PL$Lone_14= 5-PL$Lone_14
PL$Lone_15= 5-PL$Lone_15
PL$Lone_16= 5-PL$Lone_16
PL$Lone_17= 5-PL$Lone_17
PL$Lone_18= 5-PL$Lone_18
PL$Lone_19= 5-PL$Lone_19
PL$Lone_20= 5-PL$Lone_20
```

```{r}
#A general index for Loneliness#
PL$LoneGen= (PL$Lone_1+PL$Lone_2+PL$Lone_3+PL$Lone_4+PL$Lone_5+PL$Lone_6+PL$Lone_7+PL$Lone_8+PL$Lone_9+PL$Lone_10+PL$Lone_11+PL$Lone_12+PL$Lone_13+PL$Lone_14+PL$Lone_15+PL$Lone_16+PL$Lone_17+PL$Lone_18+PL$Lone_19+PL$Lone_20)/20
```

```{r}
PL$Priming=as.factor(PL$Priming)
PL$LivCamp=2-PL$LivCamp
PL$LivCamp=as.factor(PL$LivCamp)
PL$Year=as.factor(PL$Year)
PL$Major=as.factor(PL$Major)
PL$LivWith=as.factor(PL$LivWith)
```

```{r}
attach(PL)
hist(PhyAct, main="Physical Activity")
```
```{r}

```
There are outliers in PhyAct
```{r}
boxplot(PhyAct)
```
```{r}
which(PhyAct>5000)
```
```{r}
PL=PL[-c(5,21,62),]
```
Filter out the outliers: row 5,21,62.
```{r}
hist(PL$PhyAct, main="Physical Activity")
```
```{r}
```
The histogram of PhyAct without outliers.
```{r}
scatter.smooth(PL$Attention~PL$LoneGen,main="Perceived Loneliness vs Attention Question")
```
```{r}
```
It shows a positive relationship. But there are points in the top left corner and bottome right corners (responses might not pass the attention check)

```{r}
AttenCheck= PL$LoneGen-PL$Attention
boxplot(AttenCheck)
```
```{r}
which(AttenCheck>2)
```
```{r}
AttenCheck[c(6,17)]
```
```{r}
```
row 6 is the outlier in the top

```{r}
which(AttenCheck< (-0.7))
```
```{r}
AttenCheck[c(8,27,36)]
```
```{r}

```
row 8,27,36 are outliers in the bottom
```{r}
PL=PL[-c(6,8,27,36),]
```


```{r}
scatter.smooth(PL$Attention~PL$LoneGen,main="Perceived Loneliness vs Attention Question")
```
```{r}
```
Scatterplot after dropping the responses that fail the attention check.

```{r}
hist(LoneGen, main="Loneliness")
```
```{r}

```
No outliers were identified for Perceived Loneliness.
```{r}
#smoothed scatterplot
scatter.smooth(PL$PhyAct,y=PL$LoneGen,main="Perceived Loneliness vs Physical Activity")
#adding linear regression line
abline(lm(LoneGen~PhyAct,data=PL), col="red") # regression line (y~x) 
abline(v=0, col="blue",lty=2)

```
```{r}
```
Roughly linear relationship.
```{r}
#Centering around PhyAct#
PL$PhyAct.mc <- PL$PhyAct - mean(PL$PhyAct)
library(psych)
describe(PL[,c(43,44,45)])
```
```{r}
fit1= lm(LoneGen~ PhyAct.mc*Priming, data =PL) 
summary(fit1)
```
```{r}
library(interactions)


probe_interaction(fit1, pred = PhyAct.mc, modx = Priming, centered="none",
                   x.label = "Physical Activity", y.label = "Loneliness",
                   legend.main = "COVID-19 Priming", cond.int=TRUE, johnson_neyman=FALSE)
```
```{r}
boxplot(LoneGen~Priming,data=PL, main="Priming Effect on Perceived Loneliness",
   xlab="Priming", ylab="Perceived Loneliness")
```
```{r}

fit2=lm(LoneGen~ PhyAct.mc*LivCamp, data =PL)
summary(fit2)
```
```{r}
library(interactions)


probe_interaction(fit2, pred = PhyAct.mc, modx = LivCamp, centered="none",
                   x.label = "Physical Activity", y.label = "Loneliness",
                   legend.main = "Live on Campus", cond.int=TRUE, johnson_neyman=FALSE)
```
```{r}
boxplot(LoneGen~LivCamp,data=PL, main="Living on Campus or not vs Perceived Loneliness",
   xlab="Living on Campus", ylab="Perceived Loneliness")
```
```{r}
fit3= lm(LoneGen~ PhyAct.mc*LivWith, data =PL) 
summary(fit3)
```
```{r}

library(tidyverse)
```
```{r}
#Contrast coding LivWith
LivWithCon <- PL %>% mutate(LivAlone= case_when(LivWith == 3 ~ 1, 
                        TRUE ~ 0))        
head(LivWithCon[,c(10,46)],n=10)             
```
```{r}
LivWithCon$LivAlone=as.factor(LivWithCon$LivAlone)
con1 <-lm( LoneGen~ PhyAct.mc*LivAlone, data=LivWithCon)
summary(con1)
```
```{r}

library(interactions)


probe_interaction(con1, pred = PhyAct.mc, modx = LivAlone, centered="none",
                   x.label = "Physical Activity", y.label = "Loneliness",
                   legend.main = "Live Alone", cond.int=TRUE, johnson_neyman=FALSE)

```
```{r}
boxplot(LoneGen~LivAlone,data=LivWithCon, main="Living alone or not vs Perceived Loneliness",
   xlab="Living Alone", ylab="Perceived Loneliness")
```
```{r}

```

